Paper # 1 - Figures

### 2020-03-24 papers/paper-1/paper_1_figures.Rmd
v1 figures done for first paper

# Directories for the output files generated by this script
results_dir <- here::here("papers", "paper-1/")
if (dir.exists(results_dir) == F) {
  dir.create(results_dir, recursive = T)
}
```

@@

```{r}
subsidy_dat_sumaila <- read_csv(subsidy_dat_sumaila_path) %>%
  group_by(iso3, category) %>%
  summarize(subs = sum(value, na.rm = T)) %>%
  spread(category, subs) %>%
  rename(A_subs = A,
         B_subs = B,
         C_subs = C) %>%
  mutate(BC_subs = B_subs + C_subs,
         tot_subs = A_subs + B_subs + C_subs)
```

```{r}
# Calculate subsidy rates by flag
subsidy_rates_flag <- effort_totals_flag %>%
  left_join(subsidy_dat_sumaila, by = c("new_flag" = "iso3")) %>%
  mutate(A_subs_KWh = A_subs/fishing_KWh_lat_lon,
         B_subs_KWh = B_subs/fishing_KWh_lat_lon,
         C_subs_KWh = C_subs/fishing_KWh_lat_lon,
         BC_subs_KWh = BC_subs/fishing_KWh_lat_lon,
         tot_subs_KWh = tot_subs/fishing_KWh_lat_lon) %>%
  dplyr::select(new_flag, contains("subs_KWh"))

# Apply subsidy rates to binned effort
effort_binned_sub_intensity <- effort_binned %>%
  left_join(subsidy_rates_flag, by = "new_flag") %>%
  mutate(B_subs = B_subs_KWh*fishing_KWh_lat_lon,
         BC_subs = BC_subs_KWh*fishing_KWh_lat_lon,
         C_subs = C_subs_KWh*fishing_KWh_lat_lon,
         tot_subs = tot_subs_KWh*fishing_KWh_lat_lon)

# Summarize by lat/lon
subsidy_intensity_binned <- effort_binned_sub_intensity %>%
  group_by(lat_bin_center, lon_bin_center) %>%
  summarize(med_B_subs_KWh = median(B_subs_KWh, na.rm = T),
            med_BC_subs_KWh = median(BC_subs_KWh, na.rm = T),
            med_tot_subs_KWh = median(tot_subs_KWh, na.rm = T),
            mean_B_subs_KWh = mean(B_subs_KWh, na.rm = T),
            mean_BC_subs_KWh = mean(BC_subs_KWh, na.rm = T),
            mean_tot_subs_KWh = mean(tot_subs_KWh, na.rm = T),
            w_mean_B_subs_KWh = weighted.mean(B_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T),
            w_mean_BC_subs_KWh = weighted.mean(BC_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T),
            w_mean_tot_subs_KWh = weighted.mean(tot_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T),
            B_subs = sum(B_subs, na.rm = T),
            BC_subs = sum(BC_subs, na.rm = T),
            C_subs = sum(C_subs, na.rm = T),
            tot_subs = sum(tot_subs, na.rm = T),
            tot_fishing_KWh = sum(fishing_KWh_lat_lon, na.rm = T))

# Summarize by fao region
subsidy_intensity_region <- effort_binned_sub_intensity %>%
  group_by(fao_region) %>%
  summarize(med_B_subs_KWh = median(B_subs_KWh, na.rm = T),
            med_BC_subs_KWh = median(BC_subs_KWh, na.rm = T),
            med_tot_subs_KWh = median(tot_subs_KWh, na.rm = T),
            mean_B_subs_KWh = mean(B_subs_KWh, na.rm = T),
            mean_BC_subs_KWh = mean(BC_subs_KWh, na.rm = T),
            mean_tot_subs_KWh = mean(tot_subs_KWh, na.rm = T),
            w_mean_B_subs_KWh = weighted.mean(B_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T),
            w_mean_BC_subs_KWh = weighted.mean(BC_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T),
            w_mean_tot_subs_KWh = weighted.mean(tot_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T),
            B_subs = sum(B_subs, na.rm = T),
            BC_subs = sum(BC_subs, na.rm = T),
            C_subs = sum(C_subs, na.rm = T),
            tot_subs = sum(tot_subs, na.rm = T),
            tot_fishing_KWh = sum(fishing_KWh_lat_lon, na.rm = T))
```

@@

@@

```{r}
# Median
median_subsidy_intensity_tot_grid_map <- MapMaker(data = subsidy_intensity_binned,
                                                  res = "grid",
                                                  x = "lon_bin_center",
                                                  y = "lat_bin_center",
                                                  fill = "med_tot_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land)

ggsave(paste0(results_dir, "median_subsidy_intensity_tot_grid_map.png"), dpi = 200, width = 7, height = 5)

# Mean
mean_subsidy_intensity_tot_grid_map <- MapMaker(data = subsidy_intensity_binned,
                                                  res = "grid",
                                                  x = "lon_bin_center",
                                                  y = "lat_bin_center",
                                                  fill = "mean_tot_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land)

ggsave(paste0(results_dir, "mean_subsidy_intensity_tot_grid_map.png"), dpi = 200, width = 7, height = 5)

# Weighted Mean
w_mean_subsidy_intensity_tot_grid_map <- MapMaker(data = subsidy_intensity_binned,
                                                  res = "grid",
                                                  x = "lon_bin_center",
                                                  y = "lat_bin_center",
                                                  fill = "w_mean_tot_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land)

ggsave(paste0(results_dir, "w_mean_subsidy_intensity_tot_grid_map.png"), dpi = 200, width = 7, height = 5)

# Combine into three panel
intensity_tot_grid_legend <- get_legend(w_mean_subsidy_intensity_tot_grid_map)

subsidy_intensity_tot_grid_map <- plot_grid(median_subsidy_intensity_tot_grid_map + theme(legend.position = "none"),
                                            mean_subsidy_intensity_tot_grid_map + theme(legend.position = "none"),
                                            w_mean_subsidy_intensity_tot_grid_map + theme(legend.position = "none"),
                                            intensity_tot_grid_legend,
                                            ncol = 1,
                                            rel_heights = c(1,1,1,0.2),
                                            labels = c("A) Median", "B) Mean", "C) Weighted Mean", ""),
                                            label_x = c(-0.04,-0.03,-0.1,0),
                                            align = "v")

subsidy_intensity_tot_grid_map
ggsave(paste0(results_dir, "subsidy_intensity_tot_grid_map.png"), dpi = 200, width = 7, height = 12.5)

@@

```{r}
# Median
median_subsidy_intensity_tot_region_map <- MapMaker(data = subsidy_intensity_region,
                                                  res = "region",
                                                  fill = "med_tot_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land,
                                                  region_sf = fao_regions)

ggsave(paste0(results_dir, "median_subsidy_intensity_tot_region_map.png"), dpi = 200, width = 7, height = 5)

# Mean
mean_subsidy_intensity_tot_region_map <- MapMaker(data = subsidy_intensity_region,
                                                  res = "region",
                                                  fill = "mean_tot_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land,
                                                  region_sf = fao_regions)

ggsave(paste0(results_dir, "mean_subsidy_intensity_tot_region_map.png"), dpi = 200, width = 7, height = 5)

# Weighted Mean
w_mean_subsidy_intensity_tot_region_map <- MapMaker(data = subsidy_intensity_region,
                                                  res = "region",
                                                  fill = "w_mean_tot_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land,
                                                  region_sf = fao_regions)

ggsave(paste0(results_dir, "w_mean_subsidy_intensity_tot_region_map.png"), dpi = 200, width = 7, height = 5)

# Combine into three panel
intensity_tot_region_legend <- get_legend(w_mean_subsidy_intensity_tot_region_map)

subsidy_intensity_tot_region_map <- plot_grid(median_subsidy_intensity_tot_region_map + theme(legend.position = "none"),
                                            mean_subsidy_intensity_tot_region_map + theme(legend.position = "none"),
                                            w_mean_subsidy_intensity_tot_region_map + theme(legend.position = "none"),
                                            intensity_tot_region_legend,
                                            ncol = 1,
                                            rel_heights = c(1,1,1,0.2),
                                            labels = c("A) Median", "B) Mean", "C) Weighted Mean", ""),
                                            label_x = c(-0.04,-0.03,-0.1,0),
                                            align = "v")

subsidy_intensity_tot_region_map
ggsave(paste0(results_dir, "subsidy_intensity_tot_region_map.png"), dpi = 200, width = 7, height = 12.5)

## Bad Subsidies

```{r}
# Median
median_subsidy_intensity_B_grid_map <- MapMaker(data = subsidy_intensity_binned,
                                                  res = "grid",
                                                  x = "lon_bin_center",
                                                  y = "lat_bin_center",
                                                  fill = "med_B_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land)

ggsave(paste0(results_dir, "median_subsidy_intensity_B_grid_map.png"), dpi = 200, width = 7, height = 5)

# Mean
mean_subsidy_intensity_B_grid_map <- MapMaker(data = subsidy_intensity_binned,
                                                  res = "grid",
                                                  x = "lon_bin_center",
                                                  y = "lat_bin_center",
                                                  fill = "mean_B_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land)

ggsave(paste0(results_dir, "mean_subsidy_intensity_B_grid_map.png"), dpi = 200, width = 7, height = 5)

# Weighted Mean
w_mean_subsidy_intensity_B_grid_map <- MapMaker(data = subsidy_intensity_binned,
                                                  res = "grid",
                                                  x = "lon_bin_center",
                                                  y = "lat_bin_center",
                                                  fill = "w_mean_B_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land)

ggsave(paste0(results_dir, "w_mean_subsidy_intensity_B_grid_map.png"), dpi = 200, width = 7, height = 5)

# Combine into three panel
intensity_B_grid_legend <- get_legend(w_mean_subsidy_intensity_B_grid_map)

subsidy_intensity_B_grid_map <- plot_grid(median_subsidy_intensity_B_grid_map + theme(legend.position = "none"),
                                            mean_subsidy_intensity_B_grid_map + theme(legend.position = "none"),
                                            w_mean_subsidy_intensity_B_grid_map + theme(legend.position = "none"),
                                            intensity_B_grid_legend,
                                            ncol = 1,
                                            rel_heights = c(1,1,1,0.2),
                                            labels = c("A) Median", "B) Mean", "C) Weighted Mean", ""),
                                            label_x = c(-0.04,-0.03,-0.1,0),
                                            align = "v")

subsidy_intensity_B_grid_map
ggsave(paste0(results_dir, "subsidy_intensity_B_grid_map.png"), dpi = 200, width = 7, height = 12.5)

@@

```{r}
# Median
median_subsidy_intensity_B_region_map <- MapMaker(data = subsidy_intensity_region,
                                                  res = "region",
                                                  fill = "med_B_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land,
                                                  region_sf = fao_regions)

ggsave(paste0(results_dir, "median_subsidy_intensity_B_region_map.png"), dpi = 200, width = 7, height = 5)

# Mean
mean_subsidy_intensity_B_region_map <- MapMaker(data = subsidy_intensity_region,
                                                  res = "region",
                                                  fill = "mean_B_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land,
                                                  region_sf = fao_regions)

ggsave(paste0(results_dir, "mean_subsidy_intensity_B_region_map.png"), dpi = 200, width = 7, height = 5)

# Weighted Mean
w_mean_subsidy_intensity_B_region_map <- MapMaker(data = subsidy_intensity_region,
                                                  res = "region",
                                                  fill = "w_mean_B_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land,
                                                  region_sf = fao_regions)

ggsave(paste0(results_dir, "w_mean_subsidy_intensity_B_region_map.png"), dpi = 200, width = 7, height = 5)

# Combine into three panel
intensity_B_region_legend <- get_legend(w_mean_subsidy_intensity_B_region_map)

subsidy_intensity_B_region_map <- plot_grid(median_subsidy_intensity_B_region_map + theme(legend.position = "none"),
                                            mean_subsidy_intensity_B_region_map + theme(legend.position = "none"),
                                            w_mean_subsidy_intensity_B_region_map + theme(legend.position = "none"),
                                            intensity_B_region_legend,
                                            ncol = 1,
                                            rel_heights = c(1,1,1,0.2),
                                            labels = c("A) Median", "B) Mean", "C) Weighted Mean", ""),
                                            label_x = c(-0.04,-0.03,-0.1,0),
                                            align = "v")

subsidy_intensity_B_region_map
ggsave(paste0(results_dir, "subsidy_intensity_B_region_map.png"), dpi = 200, width = 7, height = 12.5)

## Bad + Ambiguous Subsidies

@@

```{r}
# Median
median_subsidy_intensity_BC_grid_map <- MapMaker(data = subsidy_intensity_binned,
                                                  res = "grid",
                                                  x = "lon_bin_center",
                                                  y = "lat_bin_center",
                                                  fill = "med_BC_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land)

ggsave(paste0(results_dir, "median_subsidy_intensity_BC_grid_map.png"), dpi = 200, width = 7, height = 5)

# Mean
mean_subsidy_intensity_BC_grid_map <- MapMaker(data = subsidy_intensity_binned,
                                                  res = "grid",
                                                  x = "lon_bin_center",
                                                  y = "lat_bin_center",
                                                  fill = "mean_BC_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land)

ggsave(paste0(results_dir, "mean_subsidy_intensity_BC_grid_map.png"), dpi = 200, width = 7, height = 5)

# Weighted Mean
w_mean_subsidy_intensity_BC_grid_map <- MapMaker(data = subsidy_intensity_binned,
                                                  res = "grid",
                                                  x = "lon_bin_center",
                                                  y = "lat_bin_center",
                                                  fill = "w_mean_BC_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land)

ggsave(paste0(results_dir, "w_mean_subsidy_intensity_BC_grid_map.png"), dpi = 200, width = 7, height = 5)

# Combine into three panel
intensity_BC_grid_legend <- get_legend(w_mean_subsidy_intensity_BC_grid_map)

subsidy_intensity_BC_grid_map <- plot_grid(median_subsidy_intensity_BC_grid_map + theme(legend.position = "none"),
                                            mean_subsidy_intensity_BC_grid_map + theme(legend.position = "none"),
                                            w_mean_subsidy_intensity_BC_grid_map + theme(legend.position = "none"),
                                            intensity_BC_grid_legend,
                                            ncol = 1,
                                            rel_heights = c(1,1,1,0.2),
                                            labels = c("A) Median", "B) Mean", "C) Weighted Mean", ""),
                                            label_x = c(-0.04,-0.03,-0.1,0),
                                            align = "v")

subsidy_intensity_BC_grid_map
ggsave(paste0(results_dir, "subsidy_intensity_BC_grid_map.png"), dpi = 200, width = 7, height = 12.5)

@@

```{r}
# Median
median_subsidy_intensity_BC_region_map <- MapMaker(data = subsidy_intensity_region,
                                                  res = "region",
                                                  fill = "med_BC_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land,
                                                  region_sf = fao_regions)

ggsave(paste0(results_dir, "median_subsidy_intensity_BC_region_map.png"), dpi = 200, width = 7, height = 5)

# Mean
mean_subsidy_intensity_BC_region_map <- MapMaker(data = subsidy_intensity_region,
                                                  res = "region",
                                                  fill = "mean_BC_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land,
                                                  region_sf = fao_regions)

ggsave(paste0(results_dir, "mean_subsidy_intensity_BC_region_map.png"), dpi = 200, width = 7, height = 5)

# Weighted Mean
w_mean_subsidy_intensity_BC_region_map <- MapMaker(data = subsidy_intensity_region,
                                                  res = "region",
                                                  fill = "w_mean_BC_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land,
                                                  region_sf = fao_regions)

ggsave(paste0(results_dir, "w_mean_subsidy_intensity_BC_region_map.png"), dpi = 200, width = 7, height = 5)

# Combine into three panel
intensity_BC_region_legend <- get_legend(w_mean_subsidy_intensity_BC_region_map)

subsidy_intensity_BC_region_map <- plot_grid(median_subsidy_intensity_BC_region_map + theme(legend.position = "none"),
                                            mean_subsidy_intensity_BC_region_map + theme(legend.position = "none"),
                                            w_mean_subsidy_intensity_BC_region_map + theme(legend.position = "none"),
                                            intensity_BC_region_legend,
                                            ncol = 1,
                                            rel_heights = c(1,1,1,0.2),
                                            labels = c("A) Median", "B) Mean", "C) Weighted Mean", ""),
                                            label_x = c(-0.04,-0.03,-0.1,0),
                                            align = "v")

subsidy_intensity_BC_region_map
ggsave(paste0(results_dir, "subsidy_intensity_BC_region_map.png"), dpi = 200, width = 7, height = 12.5)

@@

>>>>

# Version name
version <- "v1"

# Directories for the output files generated by this script
results_dir <- paste0(here::here("papers", "paper-1/"), version, "/")
if (dir.exists(results_dir) == F) {
  dir.create(results_dir, recursive = T)
}
```

@@

```{r}
subsidy_dat_sumaila <- read_csv(subsidy_dat_sumaila_path) %>%
  group_by(iso3, category, type) %>%
  summarize(value = sum(value, na.rm = T)) %>%
  group_by(iso3) %>%
  summarize(A_subs = sum(value[category == "A"], na.rm = T),
            B_subs = sum(value[category == "B"], na.rm = T),
            C_subs = sum(value[category == "C"], na.rm = T),
            BC_subs = sum(value[category %in% c("B", "C")], na.rm = T),
            tot_subs = sum(value, na.rm = T),
            fuel_subs = sum(value[type == "B7"], na.rm = T))
```

```{r}
# Calculate subsidy rates by flag
subsidy_rates_flag <- effort_totals_flag %>%
  left_join(subsidy_dat_sumaila, by = c("new_flag" = "iso3")) %>%
  mutate_at(vars(contains("subs")), list(KWh = ~./fishing_KWh_lat_lon)) %>%
  dplyr::select(new_flag, contains("subs_KWh"))

# Apply subsidy rates to binned effort
effort_binned_sub_intensity <- effort_binned %>%
  left_join(subsidy_rates_flag, by = "new_flag")

# Summarize by lat/lon
subsidy_intensity_binned <- effort_binned_sub_intensity %>%
  group_by(lat_bin_center, lon_bin_center) %>%
  summarize_at(vars(contains("subs_KWh"), "fishing_KWh_lat_lon"), 
               list(median = ~median(., na.rm = T),
                    mean = ~ mean(., na.rm = T),
                    w_mean = ~weighted.mean(., w = fishing_KWh_lat_lon, na.rm = T),
                    sum = ~sum(., na.rm = T))) %>%
  dplyr::select(-c(contains("subs_KWh_sum"), "fishing_KWh_lat_lon_median", "fishing_KWh_lat_lon_mean", "fishing_KWh_lat_lon_w_mean"))

# Summarize by fao region
subsidy_intensity_region <- effort_binned_sub_intensity %>%
  group_by(fao_region) %>%
  summarize_at(vars(contains("subs_KWh"), "fishing_KWh_lat_lon"), 
               list(median = ~median(., na.rm = T),
                    mean = ~ mean(., na.rm = T),
                    w_mean = ~weighted.mean(., w = fishing_KWh_lat_lon, na.rm = T),
                    sum = ~sum(., na.rm = T))) %>%
  dplyr::select(-c(contains("subs_KWh_sum"), "fishing_KWh_lat_lon_median", "fishing_KWh_lat_lon_mean", "fishing_KWh_lat_lon_w_mean"))
```

@@

```{r}
subs_fill_label <- "Subsidy Intensity \n($/KWh)"
```

@@

### Subsidy Intensity by 1x1 Degree

```{r, fig.width=4, fig.height=7}
# Scales 
tot_subs_fill_breaks <- seq(0,8, by = 2)
tot_subs_fill_limits <- c(0,8)
tot_subs_fill_labels <- c("0", "2", "4", "6", "\u2265 8")

# Total subsidies (grid)
subsidy_intensity_tot_grid_l <- MapMaker(data = subsidy_intensity_binned,
                                         res = "grid",
                                         x = "lon_bin_center",
                                         y = "lat_bin_center",
                                         fill = "tot_subs_KWh",
                                         fill_name = subs_fill_label,
                                         fill_breaks = tot_subs_fill_breaks,
                                         fill_limits = tot_subs_fill_limits,
                                         fill_labels = tot_subs_fill_labels,
                                         land_sf = world_land,
                                         plot_labels = c("A) Median", "B) Mean", "C) Weighted Mean"),
                                         file_name = "subsidy_intensity_tot_grid_map",
                                         file_dir = results_dir)

subsidy_intensity_tot_grid_l[["all"]]

@@

```{r, fig.width=4, fig.height=7}
# Total subsidies (region)
subsidy_intensity_tot_region_l <- MapMaker(data = subsidy_intensity_region,
                                         res = "region",
                                         x = "lon_bin_center",
                                         y = "lat_bin_center",
                                         fill = "tot_subs_KWh",
                                         fill_name = subs_fill_label,
                                         fill_breaks = tot_subs_fill_breaks,
                                         fill_limits = tot_subs_fill_limits,
                                         fill_labels = tot_subs_fill_labels,
                                         land_sf = world_land,
                                         region_sf = fao_regions,
                                         plot_labels = c("A) Median", "B) Mean", "C) Weighted Mean"),
                                         file_name = "subsidy_intensity_tot_region_map",
                                         file_dir = results_dir)

subsidy_intensity_tot_region_l[["all"]]
```

```{r, fig.width=8, fig.height=7}
# Combine into six panel
subsidy_intensity_tot_map <- plot_grid(

  plot_grid(subsidy_intensity_tot_grid_l[["median"]] + theme(legend.position = "none"),
            subsidy_intensity_tot_region_l[["median"]] + theme(legend.position = "none"),
            subsidy_intensity_tot_grid_l[["mean"]] + theme(legend.position = "none"),
            subsidy_intensity_tot_region_l[["mean"]] + theme(legend.position = "none"),
            subsidy_intensity_tot_grid_l[["w_mean"]] + theme(legend.position = "none"),
            subsidy_intensity_tot_region_l[["w_mean"]] + theme(legend.position = "none"),
            ncol = 2,
            labels = c("A) Median", "", "B) Mean", "", "C) Weighted Mean"),
            align = "hv"),

  get_legend(subsidy_intensity_tot_region_l[["w_mean"]]),
  rel_heights = c(2,0.2),
  ncol = 1)

subsidy_intensity_tot_map
ggsave(paste0(results_dir, "subsidy_intensity_tot_map.png"), dpi = 200, width = 14, height = 12.5)
```

## Bad Subsidies Only

### Subsidy Intensity by 1x1 Degree

```{r, fig.width=4, fig.height=7}
# Scales 
B_subs_fill_breaks <- seq(0,5, by = 1)
B_subs_fill_limits <- c(0,5)
B_subs_fill_labels <- c("0","1", "2", "3", "4", "\u2265 5")

# Total subsidies (grid)
subsidy_intensity_B_grid_l <- MapMaker(data = subsidy_intensity_binned,
                                         res = "grid",
                                         x = "lon_bin_center",
                                         y = "lat_bin_center",
                                         fill = "B_subs_KWh",
                                         fill_name = subs_fill_label,
                                         fill_breaks = B_subs_fill_breaks,
                                         fill_limits = B_subs_fill_limits,
                                         fill_labels = B_subs_fill_labels,
                                         land_sf = world_land,
                                         plot_labels = c("A) Median", "B) Mean", "C) Weighted Mean"),
                                         file_name = "subsidy_intensity_B_grid_map",
                                         file_dir = results_dir)

subsidy_intensity_B_grid_l[["all"]]

@@

```{r, fig.width=4, fig.height=7}
# Total subsidies (region)
subsidy_intensity_B_region_l <- MapMaker(data = subsidy_intensity_region,
                                         res = "region",
                                         x = "lon_bin_center",
                                         y = "lat_bin_center",
                                         fill = "B_subs_KWh",
                                         fill_name = subs_fill_label,
                                         fill_breaks = B_subs_fill_breaks,
                                         fill_limits = B_subs_fill_limits,
                                         fill_labels = B_subs_fill_labels,
                                         land_sf = world_land,
                                         region_sf = fao_regions,
                                         plot_labels = c("A) Median", "B) Mean", "C) Weighted Mean"),
                                         file_name = "subsidy_intensity_B_region_map",
                                         file_dir = results_dir)

subsidy_intensity_B_region_l[["all"]]
```

```{r, fig.width=8, fig.height=7}
# Combine into six panel
subsidy_intensity_B_map <- plot_grid(

  plot_grid(subsidy_intensity_B_grid_l[["median"]] + theme(legend.position = "none"),
            subsidy_intensity_B_region_l[["median"]] + theme(legend.position = "none"),
            subsidy_intensity_B_grid_l[["mean"]] + theme(legend.position = "none"),
            subsidy_intensity_B_region_l[["mean"]] + theme(legend.position = "none"),
            subsidy_intensity_B_grid_l[["w_mean"]] + theme(legend.position = "none"),
            subsidy_intensity_B_region_l[["w_mean"]] + theme(legend.position = "none"),
            ncol = 2,
            labels = c("A) Median", "", "B) Mean", "", "C) Weighted Mean"),
            align = "hv"),

  get_legend(subsidy_intensity_B_region_l[["w_mean"]]),
  rel_heights = c(2,0.2),
  ncol = 1)

subsidy_intensity_B_map
ggsave(paste0(results_dir, "subsidy_intensity_B_map.png"), dpi = 200, width = 14, height = 12.5)
```

## Bad and Ambiguous Subsidies Only

@@

```{r, fig.width=4, fig.height=7}
# Scales 
BC_subs_fill_breaks <- seq(0,3, by = 0.75)
BC_subs_fill_limits <- c(0,3)
BC_subs_fill_labels <- c("0", "0.75", "1.5", "2.25", "\u2265 3")

# Total subsidies (grid)
subsidy_intensity_BC_grid_l <- MapMaker(data = subsidy_intensity_binned,
                                         res = "grid",
                                         x = "lon_bin_center",
                                         y = "lat_bin_center",
                                         fill = "BC_subs_KWh",
                                         fill_name = subs_fill_label,
                                         fill_breaks = BC_subs_fill_breaks,
                                         fill_limits = BC_subs_fill_limits,
                                         fill_labels = BC_subs_fill_labels,
                                         land_sf = world_land,
                                         plot_labels = c("A) Median", "B) Mean", "C) Weighted Mean"),
                                         file_name = "subsidy_intensity_BC_grid_map",
                                         file_dir = results_dir)

subsidy_intensity_BC_grid_l[["all"]]

@@

```{r, fig.width=4, fig.height=7}
# Total subsidies (region)
subsidy_intensity_BC_region_l <- MapMaker(data = subsidy_intensity_region,
                                         res = "region",
                                         x = "lon_bin_center",
                                         y = "lat_bin_center",
                                         fill = "BC_subs_KWh",
                                         fill_name = subs_fill_label,
                                         fill_breaks = BC_subs_fill_breaks,
                                         fill_limits = BC_subs_fill_limits,
                                         fill_labels = BC_subs_fill_labels,
                                         land_sf = world_land,
                                         region_sf = fao_regions,
                                         plot_labels = c("A) Median", "B) Mean", "C) Weighted Mean"),
                                         file_name = "subsidy_intensity_BC_region_map",
                                         file_dir = results_dir)

subsidy_intensity_BC_region_l[["all"]]
```

```{r, fig.width=8, fig.height=7}
# Combine into six panel
subsidy_intensity_BC_map <- plot_grid(

  plot_grid(subsidy_intensity_BC_grid_l[["median"]] + theme(legend.position = "none"),
            subsidy_intensity_BC_region_l[["median"]] + theme(legend.position = "none"),
            subsidy_intensity_BC_grid_l[["mean"]] + theme(legend.position = "none"),
            subsidy_intensity_BC_region_l[["mean"]] + theme(legend.position = "none"),
            subsidy_intensity_BC_grid_l[["w_mean"]] + theme(legend.position = "none"),
            subsidy_intensity_BC_region_l[["w_mean"]] + theme(legend.position = "none"),
            ncol = 2,
            labels = c("A) Median", "", "B) Mean", "", "C) Weighted Mean"),
            align = "hv"),

  get_legend(subsidy_intensity_BC_region_l[["w_mean"]]),
  rel_heights = c(2,0.2),
  ncol = 1)

subsidy_intensity_BC_map
ggsave(paste0(results_dir, "subsidy_intensity_BC_map.png"), dpi = 200, width = 14, height = 12.5)
```

## Fuel Subsidies Only

```{r, fig.width=4, fig.height=7}
# Scales 
fuel_subs_fill_breaks <- seq(0,2, by = 0.5)
fuel_subs_fill_limits <- c(0,2)
fuel_subs_fill_labels <- c("0", "0.5", "1", "1.5", "\u2265 2")

# Total subsidies (grid)
subsidy_intensity_fuel_grid_l <- MapMaker(data = subsidy_intensity_binned,
                                         res = "grid",
                                         x = "lon_bin_center",
                                         y = "lat_bin_center",
                                         fill = "fuel_subs_KWh",
                                         fill_name = subs_fill_label,
                                         fill_breaks = fuel_subs_fill_breaks,
                                         fill_limits = fuel_subs_fill_limits,
                                         fill_labels = fuel_subs_fill_labels,
                                         land_sf = world_land,
                                         plot_labels = c("A) Median", "B) Mean", "C) Weighted Mean"),
                                         file_name = "subsidy_intensity_fuel_grid_map",
                                         file_dir = results_dir)

subsidy_intensity_fuel_grid_l[["all"]]

@@

```{r, fig.width=4, fig.height=7}
# Total subsidies (region)
subsidy_intensity_fuel_region_l <- MapMaker(data = subsidy_intensity_region,
                                         res = "region",
                                         x = "lon_bin_center",
                                         y = "lat_bin_center",
                                         fill = "fuel_subs_KWh",
                                         fill_name = subs_fill_label,
                                         fill_breaks = fuel_subs_fill_breaks,
                                         fill_limits = fuel_subs_fill_limits,
                                         fill_labels = fuel_subs_fill_labels,
                                         land_sf = world_land,
                                         region_sf = fao_regions,
                                         plot_labels = c("A) Median", "B) Mean", "C) Weighted Mean"),
                                         file_name = "subsidy_intensity_fuel_region_map",
                                         file_dir = results_dir)

subsidy_intensity_fuel_region_l[["all"]]
```

```{r, fig.width=8, fig.height=7}
# Combine into six panel
subsidy_intensity_fuel_map <- plot_grid(

  plot_grid(subsidy_intensity_fuel_grid_l[["median"]] + theme(legend.position = "none"),
            subsidy_intensity_fuel_region_l[["median"]] + theme(legend.position = "none"),
            subsidy_intensity_fuel_grid_l[["mean"]] + theme(legend.position = "none"),
            subsidy_intensity_fuel_region_l[["mean"]] + theme(legend.position = "none"),
            subsidy_intensity_fuel_grid_l[["w_mean"]] + theme(legend.position = "none"),
            subsidy_intensity_fuel_region_l[["w_mean"]] + theme(legend.position = "none"),
            ncol = 2,
            labels = c("A) Median", "", "B) Mean", "", "C) Weighted Mean"),
            align = "hv"),
